---
title: "Text Mining"
author: "Dayana Moncada"
output: html_document
---

For this post, we are going to learn how to do text mining using Gutenberg downloads - Dracula. In this project, we will be introducing new packages: -reshape2 and -wordcloud2. 

Reshape2 is a flexibly restructure and aggregate data using just two functions: melt and 'dcast' (or 'acast'). Acast or dcast, which we will use 'acast' further in this project is Use acast or dcast depending on whether you want vector/matrix/array output or data frame out- put. Data frames can have at most two dimensions.

On the other hand, wordcloud2 is a package that provides an HTML5 interface to wordcloud for data visualization.

```{r setup, include=FALSE}
library(tidytext)
library(tm)
library(dplyr)
library(gutenbergr)
library(wordcloud)
library(wordcloud2)
library(reshape2)
library(devtools)
library(blogdown)
library(ggplot2)
```


To start, let's take a look on how we can download the Dracula book and create a dataframe. 

```{r}
dracula<-gutenberg_download(345)
```

```{r}
dracula_words<-dracula%>%
  unnest_tokens(word,text)
```

```{r}
bing<-get_sentiments('bing')
```

```{r}
dracula_words<-inner_join(dracula_words,bing)
```

```{r}
dracula_words$gutenberg_id<-NULL
```

## Comparison wordcloud 

Plot a cloud comparing the frequencies of words across documents.

```{r}
dracula_words<-dracula_words%>%
  group_by(word)%>%
  summarize(freq=n(),sentiment=first(sentiment))
```

```{r}
wordcloud(dracula_words$word,dracula_words$freq,min.freq=5)
```

```{r}
wordcloud2(dracula_words)
```

```{r}
dracula_matrix<-acast(dracula_words,word~sentiment,value.var = 'freq',fill=0)
```

```{r}
comparison.cloud(dracula_matrix,max.words=100,colors=c('black', '#ff7433'))
```

## Ggplot charts 

At this point, we have become familiar with GGplot and the different data visualizations we can create with it. We divided the work between retrieving the sentiment of the words and dividing between positive and negative sentiment charts.

Positive sentiment words using dplyr:

```{r}
dracula_pos<-dracula_words%>%
  filter(sentiment=='positive')%>%
  group_by(word)%>%
  summarize(count=n(), sentiment = first(sentiment))%>%
  arrange(count)%>%
  top_n(10,wt=count)
```

Making it a factor:

```{r}
dracula_pos$word<-factor(dracula_pos$word,levels = dracula_pos$word)
```

Graph:

```{r}
ggplot()+
  geom_bar(data = dracula_pos,aes(x=word,y=count),stat = 'identity')+
  coord_flip()
```

Negative sentiment words using dplyr:

```{r}
dracula_neg<-dracula_words%>%
  filter(sentiment=='negative')%>%
  group_by(word)%>%
  summarize(count=n(), sentiment=first(sentiment))%>%
  arrange(count)%>%
  filter(word != 'miss')%>%
  top_n(10,wt=count)
  
```

Making it a factor:

```{r}
dracula_neg$word<-factor(dracula_neg$word,levels = dracula_neg$word)
```

Graph:

```{r}
ggplot()+
  geom_bar(data = dracula_neg,aes(x=word,y=count),stat = 'identity')+
  coord_flip()
```

## Combination of positive and negative sentiment in Dracula. (Graph)


```{r}
dracula_comp<-rbind(dracula_pos,dracula_neg)
```

Graph:
```{r}
ggplot()+
  geom_bar(data = dracula_comp,aes(x=word,y=count, fill=sentiment,color=sentiment),stat = 'identity')+
  coord_flip()+
  facet_wrap(~sentiment,scales='free_y')+
  scale_fill_manual(values=c('black','#ea6205'))+
  scale_color_manual(values = c('#ea6205','black'))
```

