---
title: "GGplot2"
author: "Dayana Moncada"
output: html_document
---

In this class we will learn how to create a scatter plot with the Lahman database, using dplyr, and using ggplot2, with ggiraph to make it interactive.

First let’s load some packages:

```{r}
library(Lahman)
library(dplyr)
library(ggplot2)
```

Using dplyr, we want to get all the players with 400 or more HR in their baseball careers and the total amount of SO. 

```{r}
df<-Batting%>%
  group_by(playerID)%>%
  summarize(career_HR=sum(HR),career_SO=sum(SO))%>%
  filter(career_HR>=400)
```

We need to put together the names and last names of the baseball players. 

```{r}
HR_VS_SO<-inner_join(df,Master,by=c("playerID"))%>%
  select(nameFirst,nameLast,career_HR,career_SO)

HR_VS_SO$name<-paste(HR_VS_SO$nameFirst,HR_VS_SO$nameLast)
```

To make a scatter plot with ggplo2, we use the following code:

```{r}
g<-ggplot()+
  geom_point(data=HR_VS_SO,aes(x=career_SO,y=career_HR, tooltip=nameLast, data_id=nameFirst))+
  ggtitle("Career Homeruns vs. Strikeouts for Great Mitters")+
  xlab("Career Strikeouts")+
  ylab("Career Homeruns")
```



